\documentclass[12pt]{article}
\usepackage[left=40mm, right=25mm, top=40mm, bottom=25mm]{geometry}
\usepackage{mathptmx}
\usepackage{apacite}
\usepackage{setspace}
\doublespacing

\title{Final Year Project 1 Version 4 (2018)}
\author{Nur Akmal Bin Jalil }
\date{\today}

\begin{document}

\maketitle
\pagebreak

\begin{abstract}

\noindent\textbf{Background : }Augmented Reality (AR) is a technology to make where virtual objects can be placed and manipulate in the reality environment. The purpose of this paper is to research on augmented Technology and design an educational board game. The main motivation of the board game is to teach peoples on the importance of recycling waste products and teach them the correct way to do it. Augmented Reality is one of the technology that growing rapidly and become more demand. Increasing interest of this technology creating games that is interactive and touch-less.  
\newline \textbf{Methods : }Production technique and fast prototype were using in this game.Vertical slicing technique allow the game to design with quick prototype and alterations.
\newline \textbf{Results : }Fully functional and interactive board game. 
\newline \textbf{Conclusion : }New experience of learning to design and create a augmented reality game.
\end{abstract}

\pagebreak

\tableofcontents

\pagebreak

\section*{LIST OF TABLES}

\pagebreak

\section*{LIST OF FIGURES}

\pagebreak

\section{CHAPTER 1 : INTRODUCTION}

\subsection{Overview}

\par
\subsubsection{Problem Statement}
Waste production is one of the main problem in today world. The increase of population in the world adding with the productions of materials like plastics, glass and paper to supplied the living become more presented. In the urban and industrialize countries, the problem is much worse as they produced more wastes. Waste if not manage wisely will lead to pollution and health problems. Based on the statistic  from Despite all that, urban countries develop  very effective ways manage the waste problem. One of the technique is through recycling. Recycling is define as process of converting the wastes to new materials or objects. to  In the develop country like Malaysia, the awareness for recycling is still lower among people. Malaysian government had been doing a lots of campaigns and programs to increase the awareness of recycling for the people

\par

Augmented Reality or mixed reality is the technology of enhancement of the real world with a set of virtual objects in it. Augmented reality technology is person's real environment is supplemented or augmented with computer-generated images usually motion tracked. Augmented reality technology is getting more popular and demand today. One of the example where augmented reality technology getting renown through the mass is when  the Pokemon GO \cite{PokemonGo}, a mobile games launch. The massive popular franchise adding with new technology, that is augmented reality make this game so popular. Another example is the application features that can found in Snapchat application called Snapchat filter. This features allow images to be render in the user camera. Image like cat and dog ear is very popular among users. Currently augmented reality also showing promise with efforts like Microsoft's Hololens and their own secret projects. After that, many game developer and mobile application try to develop augmented reality game and application. The future of the augmented reality is very promising and because of that, this project will focusing in integrating augmented reality into the project. 

\par 

The term of augmented reality is contributed by former Boeing researcher, Thomas P. Caudel in 1990 \cite{lee2012augmented}. Augment is from the Latin word \textit{augere}, meaning to "increase" or "to add", hence Augmented reality can define as adding or increase people existing reality. Augmented reality act as a digital addition to user's world, for example digital object can appear on tables, informations can be displayed in floating windows and graphics can be generated all seamlessly motion tracked to user field of view. The augmented reality is different because this technology directly affects the perception and processes of the human mind in an obvious way and only technology that can provide actual packaged experiences. This technology become more powerful this time around and more feasible. At current rate, by 2025 attractive AR technology will be commonplace if done right. Augmented Reality technology show incredible potential.

\par

Many articles have been published in the last 20 years on video games for learning, and several reviews of the literature on educational games have been completed within the last few years . However, these reviews focused on literature that addressed what players learn from video games rather than how video games can be designed to facilitate learning. This review focuses on publications addressing educational video game design, seeking to identify elements of game design that promote learning as well as the learning theories that conceptualize how video games foster learning.

\subsection{Problem Statement}

\subsubsection{Aims and objectives - Initial Project Brief}

Augmented reality is the future of the technology hence, this project will develop board game integrated with augmented reality. The game also will be focusing in educating while playing. the board game is selected as the main game genre is because the board game allow players to sit and play together in one place. As this game is mainly focusing on educating, the board game can be a platform for teachers or family to teach their students and family members respectively. For the education subject, this project choose recycling waste awareness as the centre of interest. Recycling waste was chosen as the awareness of this activity is still low around Malaysian. This game will allow the player to Initially, In this paper, the development strategies will be proposed.

\subsection{Project Scope}

\begin{enumerate}
    \item Goals
    \newline
    Several goals has been decide to be on the early stage of the project. The project will use the goal as the benchmark for the the development later. 
    \begin{itemize}
        \item Augmented reality board game
        \newline
        The first goal of this project is to deliver fully functional augmented reality board game. The game will have interactive game play and  interface that give immersion to players while player play with it.
        \item Educating content
        \newline
        The project also will try to deliver an effective educating content that can beneficial to the players. The players will not just going to have fun while playing with it, but also get great information about the subject matters. The fun element will make the players to remember the subject much longer and will make the players at ease while applying in the real world.
    \end{itemize}
    \item 
\end{enumerate}

\pagebreak

\section{CHAPTER 2 : LITERATURE REVIEW}

\subsection{Early Augmented Reality Technology}
In the early patent of augmented reality  \cite{meisner2007augmented}, augmented reality is define as tracker system for determining the relative position between a sensor and a object surface.This technology use the sensor system to detect a pattern in the surface and process objects to be shown in the surface.An early patent also describe the augmented reality technology consist of pattern of fiducial disposed on an object surface, processor inside the computer or the mobile phone, user interface for receiving output from user, and lastly a tracker for detecting the pattern. The methods that patent use is by tracking the position and orientation of an object generally by scanning across an object to detect fiducial and form video run. It also clustering video runs to detect pattern of fiducial, obtaining the estimated values for a set of tracking parameters by comparing a detected patterns of fiducial to a reference pattern of fiducial. Next, the early patent method repeating the estimated values for the set of tracking parameters until the detected pattern of fiducial match the reference pattern of fiducial to within a desired convergence.

\subsection{Augmented Reality technology in the current year}
Augmented reality is one of the biggest technology in 2018 \cite{some99} alongside virtual reality. The technology, which overlays digital information into viewer's reality physical world, has been popularized by the like of Pokemon GO. But Augmented Reality had gone much deeper that that thanks to recent development from Apple, Google, Facebook, and Snapchat amongst others. Despite all that, mass adoption won't happen for a couple of years as developers get the grips with the new access and ecosystem. Compare to virtual reality, which has around 82 million units around the world, AR peak at over three billion thanks to the augmented reality tech integrate to the smart phone today make it more accessible to people. With that many devices already in the people's hand, AR industry is worth between 20\$-162 billion. The future of AR is open now and the big guns have unveiled their platform, like Apple's ARKit, Google's ARCore, and Snapchat Lens Studio. This allowing the developers to create their own augmented reality apps and features. more tools and layers are expected to be see in the near futures as phone and photo-altering filters. Example, is like seeing the directions to where the nearest defibrillator as in medical emergencies. Virtual reality still has a huge part to play in the future of gaming and education, but the hefty price tag in the high-end devices and consumer expectation versus reality are powerful detractor that will slow adoption of VR. the issues for many AR technologist and consumers is the need to view the added graphic to the screen, which can detract from being in the moment. In the near future when the arrival of smart contact lens that now has been develops by the Google we will see more of augmented reality. As smart lens is still under development, Magic Leap has been in action in today augmented reality technology. Magic Leap, a secretive startup based away from silicon valley in Florida has working with mixed reality. Instead of brand new virtual world, the visor will give the user information that can be added and floating in the air. After years of teasing with the tech, the company has finally announced that the Magic Leap One Creator Edition is coming in 2018 for developers, sending shockwave through the industry. The initial hardware offering consist of a small computer, powering pair of goggles and the user wears. If the technology is good, it will evolving the industry. 
Across mixed reality and virtual reality, the advertising and start-up world are interested  for more space where they can be personally target and use data to retarget users. Advertiser soon can start using eye tracking system capabilities to determine interest levels. A short film by Keiichi Matsuda called 'HyperReality' sum up the depicting world where "physical and virtual realities have merged, and the city is saturated in media". As the technology improved each years, a lots of new player will come out into the market. According from the data from RetailPerception \cite{impat77}, 40\% of the people would pay more if they can test in AR first. Expect retail to be the first-movers and the innovators in the space, as they have the most gain. Already in the place like IKEA, letting potential buyer to plonk digital furniture into their living room, to Specsaver's try them on glasses AR tool. The future of AR, as the most new technologies, will go down one of two roads, everydays usage that become more invisible, or a nice to have technology that never took off. Hype from the customer interest may increase the investment level. 2018 become the year where the AR will strech into the new direection, bringing a lot more people into the game. More investment will set up in near future of AR technology.

\subsection{Augmented Reality in Education}
Many form of education today have become more sophisticated and interactive. One of the form of education today is through augmented reality. One of the reason of using augmented reality as education platform is not just the technology able to show three-dimensional virtual objects but also it ability to be used to enhance collaborative tasks \cite{billinghurst2002augmented}. In the paper, the author offered augmented reality as educational purpose as the technology support seamless interaction between real and virtual environments, the use of a tangible interface as similitude for object manipulation, and also it ability to transition smoothly between reality and virtuality. For seamless interaction, as students mostly inside the classroom will have difficulty to focused on a same workspace as they working in different computers. Even when seated in same computer, group communication pattern still will be different. When students work at a same table, they can use same space to sharing communication like gaze, gesture and nonverbal behaviors. If the people are talking about the objects on space of the table, then task-space is a subset of the communication patterns. The collaborators can see each other and shared communication cues at the same time, while discussing about the objects. In this case, the task space is separated from the interpersonal communication. In disparity, in an augmented reality interface students can seated around the table together and see each other at the same time as a virtual objects floating in the mid.

\newline

\par

For tangible interface metaphor, the augmented reality has intimate relationship between virtual and physical objects. The physical objects can be enhanced in way that normally it has been by giving dynamic information overlay, private and public data display, context sensitive visual appearance and physically based interactions. This attributes using physical objects to manipulate virtual information in an intuitive manner

\par In the paper \cite{lv2015touch}, the augmented reality technology was used to creating pervasive game. The game allow the users to interact with augmented reality games using dynamic hand and feet gestures in front of the camera. The interaction will trigger the event for the virtual object in the scene of the game. The game represent an exciting development in playing games. The use of sensor, visualization and networking technologies issues immerse live-action game experiences and expand the game experience out into the real world. Pervasive game application include variety range from daily life to education , city experience, cultural heritage, library exploration, environmental sustainability, office spaces, mobility training, tourist, traffic and game mastering.In the paper the game use system that integrated two parts on human-centered design. First is vision-based wearable hardware and touch-less interaction-based augmented reality game software. The paper also discuss the use of gesture recognition algorithm. This algorithm use dynamic programming-based CTM algorithm that localize hand and foot skin contour.% [EDIT] This is conclusion, need to write the more
The paper conclude a series of designed gestures and the research evaluation related to touch-less interaction technology on vision-based wearable device. The paper also provides a low-cost solution for the professional augmented reality games on mobile phone.
\par The majority of the game that we have in the market today intend to provide the entertainment and enjoyment to the players, yet many developers also try to slide some educational to the game. In the paper \cite{dondlinger2007educational}, the author emphasize that many attention as been directed to use of the video games for learning and education. The ability of the video games to captive player attention and take lengthy time to learn and master the game complexities and objectives.
%[EDIT]

\subsection{Augmented Reality in Game Development}

\subsection{Type of Augmented Reality}

location-based
\newline
maker-based

\subsection{Software Developer Kit (SDK) for Augmented Reality}

\begin{enumerate}
    \item ARToolKit
    \item EasyAR
    \item Wikitud
    \item Kudan
    \item ARKit
    \item ARCore
    \item Vuforia
    \item Maxst
    \item DeepAR
    \item Xzimg
\end{enumerate}

\subsection{Gamification}
Game production becoming more rapid in the recent years. The existing of the mobile phone, creating mobile application games leading to mass production of games. Even thought many consoles and computer games still thrive in games production race, mobile game that more easy and casual attract a lot of new demographic of game players. Through the existing of more game players, many developer try to integrate education to the game. Education in the game can be new way of teaching kids and adult in more enjoyable. Gamification is a word that come from the combination of word game and education. Gamification \cite{deterding2011game} can be summarized as connecting the human-computer interaction and game studies, such as serious games, pervasive games

\par The true purpose of design and making this game is 


\subsection{Understand Tabletop Game Genre}
This project is all about the board game using AR technology. Before designing the board game, researching on board game design is essential. While board game share many ideas with video games, they are played in a very different way, and often use very different game mechanics. Designing a board game can be a challenging test.In the article , board game design is started by classify the genres of the board game. By classify the genres, it help understand more about different types of board games. Example of board game genres are:

\begin{itemize}

\item Classic Board Game or Family Games
\\ These game require the players to race to the final goal. Sometimes, involved points system. This game heavily relies on luck and not a strategy. Main purpose of this kind of the game is usually have an experienced to play the game in together. Most of the time, these game have very simple or absurb theme which not have strong impact on the game mechanics. Examples of these games are Snakes and Ladders, Candyland
\item Euro-Style Games
\\ These game are often about gaining the victory points, an arbitrary resources that allows you to win. Usually the game has certain number of turns to end the game or continue until player has certain number of victory points/ These game has strong themes which inform much of the design. There is also usually a system of resources management. Player can also engage with one another to negotiate the sale and trade resources. Luck is not heavily effect these kind of games, as the games has fewer elements of luck and chance. Examples of the games are Settlers of Catan, Power Grid, Carcassone, and Lancaster.

\item Deck-Building Games
\\ Deck-Building Games(DBGs) are similar ti Trading Card Game(TCG) where each players have a deck of cards they use during play. The difference is that in DBGs he players all work from the same card collection, and the deck-building occurs as part of the game. These games usually come with 15-20 different card types, but only ten are used in a single game. This gives the games a lot of replay value. In these games players build their deck over time by purchasing available cards from the pool of cards. Games like this usually end when a certain number of card types are depleted, or when a specific situation occurs.
Examples of these type of games are Dominion, Thunderstone, Nightfall, and Quarriors

\item Abstract Strategy Games
\\ Games like Chess and checkers are consider abstract strategy games. The point of this game is where the two players will have a strategic battle in where they must out-think their opponent. These games are harder to describe without specific examples, and the game elements and goals are not quite as common across the genre. Instead of dice rolls or card combinations, the goal is often to position pieces in just the right location.Examples of this games are Chess, Checkers, Quoridor, and Push Fight

\item Strategy Games
\\Strategy games are much grander Euro-style games. These games usually have a very important board and a narrative which drives the game's progress. These games often involve a heavy amount of co-op and competitive play, forcing players to make and break alliances over the course of the game.Players are usually participating as much in the game itself as they are in higher-level mind-games with each other: trying to get ahead, form alliances, and discern their opponent's motives. These games are generally marked by very long game sessions (six hours or more, for some), and are sometimes affectionately referred to as "friendship-ending games", because of how passionate players become. Risk is perhaps the most well-known game in this genre.Examples of these games are Risk, Twilight Imperium, Arkham Horror, and Battlestar Galactica

\item Card-Based Strategy Games
\\Card-based strategy games are strategy games where cards are the primary game element. Games like this vary heavily, but there is often a drafting mechanic, or an element of character or base building where players use cards to gain abilities or bonuses. These games usually have a heavy element of luck or randomness.The goal in games like this can be based on victory points, trying to complete a specific set of cards, or eliminating certain target players, among others. Games like Poker, Spit, and Egyptian Rat Screw don't fit into this category because they lack a central theme, and don't require anything other than a standard deck of cards. Deck-Building Games could fit into this category, but have become so popular I consider them their own genre.Examples of these games are Munchkin, Bang, 7 Wonders, and Chrononauts

\end{itemize}

\subsection{Designing a Tabletop Game}
In the article \cite{design423}, the first step to design a tabletop game is to coming up with the idea. A great way to get inspired for the idea is to take a look at game that already in the market. By trying to add or remove elements of the existing game, new perspective can be achieved. When adding and removing something from the game, looking at the components become more critical. When remove the elements, it is much easier to look at elements that important or unimportant. This can give the deeper understanding of the game. Another great technique is to start with theme and system that is favorable. Start working at specific theme or system will make it easier to determine game play to be implement. 

\subsection{Video Game Development Process}
Developing an video game is not an easy task. The development of video game is a long and tedious one \cite{game09}. For this reason very thorough and detail design need to be implement. Many video game developers create a very good game development process technique. One of the development process technique is by dividing the process into four chronological parts. First is the game concept, then pre-production, production and lastly a post-production. Each stage is very important the development process can be run smoothly.

\par

Game Concept stage is an idea stage for game development. Game concept acts ans blueprint for the entire game production. This stage is where the idea is generated and deciding the genre of the game. The concept chosen can be an original idea, a sequel, or a licensed-based title. License based-titled can be based on books, movies, or some specific people. Once all the ideas has been decided, concept plan need to be revise to have the final decision concept. The process needs to be efficient right from the conceptualization stage.

\par

After concept process has been finalized, more detailed design document of the game is generated. This mostly done by the game designer. This stage is called pre-production. This stage, the document specifies the primary aims of the game, and tries to establish, in cohort with the everyone making the game. This to ensure, the design is actually realistic and achievable or not. If is not achievable, certain tweaks can be made to the primary design. Once it has been established that the game can be achieved, the programmer come to the picture. The programmer will start working on the development software and also produce a highly detailed technical report, explaining what kind of technology will be used for making the game, and what kind of engine it will work on. Schedule plan also will be make for each task is expected to completed in. This stage require ability to work under extreme pressure and meets a lot of deadlines, and at the same time produce the best quality of work possible.

\par

Production is the most important part of the stages, and the one area where the maximum expertise is required. This is the phase where the need of tools programmers, the engine programmers, the user interface programmer, and the artificial intelligence programmers all working in sync with each other. The animators and the artist will working on the visualization and animation of the assets. The audio department the then adds all the suitable sounds effects and noises needed for the game. The voice of the characters, the background music, the interface music and other things are what the people from this department will work on. The cost of the best equipment and machinery used for the making of this game will be calculated. The cost of development can run very high due to large number of developers. The producer and the manager simultaneously review all the works during this time. They also carrying out the detailed risk assessment in the market, and trying to predict how well the game will do.

\par

Post-production is the last stage for the process. Testing is the main process in this stage. Once game has been developed, testers are required to play it and highlight the bug that may inside. If bugs is found, the necessary step needed to incorporated. The graphics and the game-play are the tweaked and polished, and it is ready to be sent to the manufacturers. Marketing of the video game is very important, and this is something that keeps happening all along, during the development process. The developers are contracted to reveal anything about the game though, as this could ruin the response of the consumers. Once it is released, the task is accomplished.

This is not the end of the matter though, as some faults will only arise once gamers start using it. If there are any such faults, then necessary patches must be released over the Internet so that everyone is satisfied with the final product. The biggest video game production houses spend a lot of time, energy, and money, as it is the attention to details that ultimately makes all the difference.
% Edit start

% Edit end
\subsection{Vertical Slicing}
% Edit start



% Edit end
\subsection{Recycling in Malaysia}
% Edit start

% Edit End

\pagebreak


\section{CHAPTER 3 : GAME DESIGN AND CONCEPT}

\subsubsection{Game Overview}
The primary objective of the game is for the player to compete with each other or with the computer to get the highest points. In the game, the materials will randomly spawn inside the tile in the map. The player need to move from tile to tile according to the number of points get from throwing the dice. The player need to sorting the materials into the right types and send it into the recycle bins. This section elaborates on the description of the game play and user controls.

\subsubsection{Game Description}
In the game, the player is played as a character that will move and explore all the map called the "throw-in's city". The player will move in turn using the dice. In this city, every blocks or tile map will spawn materials randomly in every turns. The player will collect every materials that was been visited. The player then need to sort the materials into four different type: plastic, glass ,paper ,and non-recyclable. Every materials that recycle correctly will grant points. If the player sort incorrectly, the points will be deduct. Every turn the uncollected materials in the tile map will be transfer in garbage's area. 

\subsection{Game Genre}
This game is a board game with main genre of resources management. The theme of the game is recycling waste using the three principle of recycling that is recycle, reduce and reuse.  

\subsubsection{Target Audience}
This board game targeting family as main audience. As family can gather together to play together and at the same time teaching each other about important of recycling. Educator also like teachers can use this game as medium to teach their students about the recycling. This board game has the 

\subsubsection{Core Game Play}
The core game play of this game will use the three principles of recycling that is reduce, recycle and reuse (3R). 
\begin{itemize}
    \item Player can throwing dice and move around the board according to the number of the dice. When move around the board, the player will collects all the garbage they encountered. This use the first principle of the recycling that is reduce.
    \item The player can sorting the garbage into the correct materials according to their colors of the recycle bin. The points will allocated to the player if the player correctly sorting the garbage into the correct recycle bin. This use the second principles of recycling that is recycle. The player can only add recycle bin inside the board using points. 
    \item The last principle that integrate into the game play is reuse. Player can combine the materials that they collected into new materials. It will give points for every combined items.
    
\end{itemize}

\subsubsection{Game Flow}
\begin{enumerate}
    \item The player place the avatar in the corner of the board.
    \item The player have beginning of 500 points.
    \item The player throw two dice. Movement tiles will shown up on the board depends on the number of the dices, allowing player to move around.
    \item While moving around the tile, players will collected all the garbage in the tiles they contacted to. 
    \item Player then need to put recycle bin inside the tile. Doing that need to use 20 points for every bin. It important for player to put recycle bin because it the only way the players can recycle the materials they collected before. 
    \item After player put recycle bin inside the tile, the bin cannot be remove and if other players need to do recycling in the tile, they need to give half of the points they got to the owner of the bin.
    \item The player also can combine the garbage into new materials. The points will allocated to player for every materials created. Points value also depends on the materials that been created.
    \item By doing this, player can also exchange materials with other player allowing player to strategies their game play.
    \item After collecting the garbage three times the tile will not producing garbage anymore and the tile consider clean.
    \item if the garbage is not collected in the tile for more than three times, every players will be punished by reducing some of their points. 
    \item If all garbages inside the tiles has been collected, the game is officially end and the players with highest points win the game.
\end{enumerate}


\pagebreak

\section{CHAPTER 4 : RESEARCH METHODOLOGY}






\subsection{Development process}
The development process for the game of this project are basically divided into four chronological stage. The first stage is the concept stage, the pre-production, the production, and the post-production stages. 
\subsection{Game Concept}

Every game project needs an idea and concept before it can be develop. The game concept acts as blueprint of the entire game project.

\subsection{Pre-production}

\subsection{Production}
\subsection{Post-production}
\subsection{Implementation}
\subsubsection{Using Unity3D}
For the development of the  game, Unity3D engine was chosen to become the main engine. Unity3D is proved to one of the game engine out there that is open source and beginner friendly. Using C as the main scripting language as C was one of the popular scripting language in game development. 
\subsubsection{Using Vuforia}
\subsubsection{Using Blender}
For the 3D modelling, Blender software will be used. Blender is open source software that allow user to create, model, and render 3D models. 
\subsection{Software for Augmented Reality}
\subsection{Design the game}
\subsection{Game Version and Testing}

\pagebreak

\section{CHAPTER 5 : IMPLEMENTATION PLAN}
\subsection{Gantt Chart}
\pagebreak

\section{CHAPTER 6 : CONCLUSION}
\pagebreak

\bibliographystyle{apacite}
\bibliography{fyp.bib}
\end{document}
